---
title: "The Start"
format:
  html:
    code-fold: true
execute: 
  warning: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(broom)
library(scales)
library(forcats)
library(zoo) 
library(plotly)
library(ggthemes)
```

## A Growing Desire to Emigrate Out

The COVID-19 outbreak in 2020 has fuelled an increase in the urban youth's desire to leave China. This is due to severe lockdown measures disrupting daily life and causing panic, hastily introduced government policies like the 'Three-Child Policy' and 'Double Reduction Policy' adding societal and economic pressures, and increasing burdens on people, notably women and parents. Additionally, shrinking opportunities for educational upward mobility, expanding censorship, worsening Western diplomatic relations, and fears of further international isolation due to the pandemic have made emigration more attractive to younger generations.

In this context, the concept of “Rùn” has gained significant traction. ***"Rùn"*** is a term currently being utilized interchangeably with the English word 'run' to symbolize a strong desire to emigrate out of China. The term has become especially popular among Chinese urban youth, who long for a future where they can live autonomously without being chained to societal pressures and have a reasonable level of control over their lives. Their will to “run” often represents the pursuit of freedom, individual autonomy, better opportunities, and a less stressful lifestyle. Women of reproductive age, in particular, have shown a significant interest in “Rùn” as they face additional societal stressors like age-based and maternity-based discrimination in employment, gender inequality, and the pressure to have up to three children due to China's new policy. 

Amidst these circumstances, the emergence of “zouxian,” a risky journey involving Chinese people walking through South and Central America to enter the US via its Southern border, can be understood as an extreme, desperate manifestation of the desire to "Rùn."

```{r}
## Prepare google trends data for plotting
trends <- read_csv("data/google_trends.csv")
colnames(trends) <- c("Week", "Search_Emigrate", "Search_Zouxian")

## Convert Week to Year and Month and
## Get the sum of search for each month
trends <- trends %>% 
  mutate(Date = as.Date(Week, format = "%m/%d/%y"),
         Year = as.numeric(format(Date, "%Y")),
         Month = as.numeric(format(Date, "%m")),
         Search_Emigrate = as.integer(Search_Emigrate),
         Search_Zouxian = as.integer(Search_Zouxian)) %>% 
  group_by(Year, Month) %>%
  summarise(Search_Emigrate = sum(Search_Emigrate, na.rm = TRUE),
            Search_Zouxian = sum(Search_Zouxian, na.rm = TRUE)) %>%
  ungroup() %>% 
  mutate(Date = paste(Year, Month, sep = "-")) %>%  # Combine year and month to Date
  select(Date, Search_Emigrate, Search_Zouxian) %>% 
  # Remove the last row as it is incomplete
  filter(Date != "2023-12")
  

## Stardardize the Search_Emigrate using min-max normalization and ajust the scale scale for Search_Zouxian accordingly
range = max(trends$Search_Emigrate) - min(trends$Search_Emigrate)
trends <- trends %>% 
  mutate(Search_Emigrate = 100 * (Search_Emigrate - min(Search_Emigrate)) / range,
         Search_Zouxian = Search_Zouxian * (100/range))


## Plot the google trends data with a line chart
trends$Date <- gsub("-(\\d)$", "-0\\1", trends$Date)
trends$Date <- as.yearmon(trends$Date, "%Y-%m")
breaks <- seq(min(trends$Date), max(trends$Date), by = 4/12)

p <- ggplot(trends, aes(x = Date)) +
  geom_point(aes(y = Search_Emigrate, color = 'Search_Emigrate'), size = 1.5 ) +
  geom_line(aes(y = Search_Emigrate, color = 'Search_Emigrate'), size = 1) +
  geom_point(aes(y = Search_Zouxian, color = 'Search_Zouxian'), size = 1.5 ) +
  geom_line(aes(y = Search_Zouxian, color = 'Search_Zouxian'), size = 1) +
  geom_rect(aes(xmin = as.yearmon("2020-01"), xmax = as.yearmon("2020-04"), ymin = -Inf, ymax = Inf), fill = "lightgrey", alpha = 0.01) +
  geom_rect(aes(xmin = as.yearmon("2022-02"), xmax = as.yearmon("2022-08"), ymin = -Inf, ymax = Inf), fill = "lightgrey", alpha = 0.01) +
  ggplot2::annotate("text", x = as.yearmon("2020-02")+0.1, y = 93, label = "Wuhan \nLockdown", color = "black",size = 3, family="Charter") +
  ggplot2::annotate("text", x = as.yearmon("2022-05"), y = 93, label = "Shanghai \nLockdown", color = "black", size = 3, family="Charter") +
  scale_x_yearmon(breaks = breaks, labels = date_format("%Y-%m")) +
  labs(title = "Monthly Search Popularity for Emigration and \"Zouxian\" 2020-2023",
       subtitle = "Major city lockdowns to manage the pandemic sparked a surge in online searches.",
       x = "Date", y = "Google Search Popularity \n(Peak of the search for \"emigrate\"=100)") +
 ggplot2::annotate("text", x = Inf, y = 0, vjust = 6, hjust = 1.2,
            colour = "black",
            label = "Source: Google Trends", size = 3, family="Charter") +
  coord_cartesian(clip="off") +
  theme_hc() +
  theme(axis.text.x = element_text(angle = 0),
        text=element_text(size=11,  family="Charter"), 
        legend.position = c(0.85,0.85),
        legend.title = element_blank(),
        legend.spacing.x = unit(0, "cm"),
        legend.spacing.y = unit(0, "cm") 
        ) +        
  scale_color_manual(values = c('Search_Emigrate' = 'darkblue', 'Search_Zouxian' = 'darkorange'))

p

```
## Reasons to "Rùn" 

The decision to leave China permanently is driven by a myriad of factors. First, economic opportunities often lure Chinese citizens to emigrate. Many are attracted by a higher standard of living and better job prospects. Second, they aim to provide a better environment for their children, with desirable overseas education and healthier upbringing conditions being highly valued. Moreover, the safer and more regulated social atmosphere, the protection under the rule of law, and more personal and political freedoms in other countries serve as significant pull factors. These rights and legal protection, which might be lacking or inconsistent in China, are crucial attractions for those considering permanent departure.

For those resorting to the extreme "zouxian" option, it is often the culmination of a sense of desperation and lack of alternatives. Due to restrictive visa policies, financial constraints, or lack of assets that could facilitate safer immigration options, they see "zouxian" as their only avenue for leaving. Despite the inherent risks, these individuals feel compelled to take the leap, reflecting the extent of their dissatisfaction and desperation within the prevailing circumstances in China.

Voice of America (VOA) presents a series of valuable insights through interviews conducted with successful emigrants in various countries, including Thailand, Australia, and the U.S. These narratives encompass diverse emigration methods, including illegal border crossing. By examining their experiences and motivations, we can better understand the prevailing reasons driving the Chinese people's legal or illegal emigration.


```{=html}
<iframe src="https://zj117.shinyapps.io/voa_topics" style="border: none; width: 750px; height: 600px"></iframe>

```

<br></br>
[Interviews (in Chinese): VOA](https://projects.voanews.com/china/runners-without-borders/){target="_blank"}
